---
title: "SRT411A0"
author: "Volodymyr Nahirnyi, Github username: VolodymyrNahirnyi"
date: "February 16, 2018"
output:
  pdf_document: default
  word_document: default
  html_document: default
---
This assignment is based on the excercises from "A (very) short introduction to R", available at 

https://cran.r-project.org/doc/contrib/Torfs+Brauer-Short-R-Intro.pdf

RStudio was used to write the code, the document was created using Knitr engine that generated a Markdown report. This report was then converted to PDF with Pandoc converter.
This documends includes several R code chunks and their results (data or charts). The additional resources that were used are:

https://rmarkdown.rstudio.com/

https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf

https://nicercode.github.io/guides/reports/

### ToDo 1
```{r}
(2016-2014)/(2014-2000)*100
```

### ToDo 2
```{r}
a <- 2016
b <- 2014
c <- 2000
d <- 100
(2016-2014)/(2014-2000)*100
```

### ToDo 3
```{r}
vector <- c(4,5,8,11)
sum(vector)
```

### ToDo 4
```{r}
x <- rnorm(100)
plot(x)
```

### ToDo 5
```{r}
help(sqrt)
```

### ToDo 6
```{r}
x <- rnorm(100)
write(plot(x), file="filescript.R") 
source("firstscript.R")
```

### ToDo 7
```{r}
P = seq(from=31, to=60, by=1)
P
Q = matrix(data=seq(from=31, to=60, by=1), nrow=6, ncol=5)
Q
```

### ToDo 8
```{r}
x1 <- rnorm(100)
x2 <- rnorm(100)
x3 <- rnorm(100)
t <- data.frame(a = x1, b = x1+x2, c = x1+x2+x3)
plot(t)
```

### ToDo 9
```{r}
x1 <- rnorm(100)
x2 <- rnorm(100)
x3 <- rnorm(100)
t <- data.frame(a = x1, b = x1+x2, c = x1+x2+x3)
plot(t$a, type="l", ylim=range(t),
lwd=3, col=rgb(1,0,0,0.3))
lines(t$b, type="s", lwd=2,
col=rgb(0.3,0.4,0.3,0.9))
points(t$c, pch=20, cex=4,
col=rgb(0,0,1,0.3))
```

### ToDo 10
```{r}
d <- data.frame(a = c(1,2,4,8,16,32), g = c(2,4,8,16,32,64), x = c(3,6,12,24,48,96))
write.table(d, file="tst1.txt", row.names=FALSE)
d2 <- read.table(file="tst1.txt", header=TRUE)
d2$g <- d2$g * 5
write.table(d2, file="tst2.txt", row.names=FALSE)
```

### ToDO 11
```{r}
v <- c(rnorm(100))
mean(sqrt(v))
```
There is no square root of a negative number, therefore negative numbers from this vector are not available and we get this output.

### ToDo 12
```{r}
dates <- strptime( c("20180216", "20141206", "20180325"), format="%Y%m%d")
presents <- c(0,3,5)
plot(dates,presents)
```

### ToDo 13
```{r}
v <- seq(from=1, to=100)
  for(e in v)
  {
    if(e < 5 | e > 90)
    {v[e] <- e * 10}
    else{
      v[e] <- e * 0.1
    }
  }
v
```

### ToDo 14
```{r}
fun = function(arg1)
  {
  l = length(arg1)
  for(e  in 1:l)
    {
      if(e < 5 | e > 90){
        arg1[e] <- e * 10
      }
      else{
        arg1[e] <- e * 0.1
      }
    }
  return(arg1)
  }
fun(arg1 = v)
```

### ToDo 15
```{r}

```
